---
title: "Report Title"
author: "Data and Performance Team (OEWD)"
date: "`r Sys.Date()`"
self-contained: true
format: 
  html:
    output-file: "REPORT_TITLE"
    output-ext: "html"
    toc: true
    css: style.css
    page-layout: full
execute: 
  echo: false
  warning: false
  message: false
---

```{r}
library(gt)
library(tidyverse)
```

# Overview

Unordered list:

-   Item 1
-   Item 2

::: callout-note
This is a callout note.
:::

# Analysis

```{r}
#| fig.cap: 'Figure 1: MPG vs horsepower, colored by transmission.'
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth() +
  theme(legend.position = 'bottom')
```

# About this Report

This HTML report was created with [Quarto.](https://quarto.org/) The data within is self-contained and cannot be updated automatically. If you bookmark the report within your browser, be aware that the bookmark URL references a file path on your computer; moving the document to a different location will break the bookmark.
